---
title: "Chp1 Q13"
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
a).
Verify the 95% LR confidence interval
```{r}
library(binom)
binom.confint(x = 4, n = 10, conf.level = 0.95, methods = 'lrt')
```

b).
```{r, warning=FALSE}
#true confidence levels can be found using 'binom' package
library(binom)
binom.coverage(p = 0.4, n = 10, conf.level = 0.95, 
               method = c("asymptotic", "agresti-coull", 
                          "wilson", "exact"))

binom.plot(n = 10, method = binom.asymp, np = 500, conf.level = 0.95, main = "Wald")
binom.plot(n = 10, method = binom.agresti.coull, np = 500, conf.level = 0.95, main = "Agresti−Coull")
binom.plot(n = 10, method = binom.wilson, np = 500, conf.level = 0.95, main = "Wilson")
binom.plot(n = 10, method = binom.exact, np = 500, conf.level = 0.95, main = "Clopper−Pearson")
```

c).
According to the graphs in b), the Wilson interval and the Agresti-Coull interval performs very good, with Wilson interval to be slightly better than Agresti-Coull.

The Wald interval performs the worst, because is tends to be very far away from 0.95 the most often.

The Clopper−Pearson performs too conservative. The true confidence level is mostly between 0.96 to 0.995.

The Wilson interval performs slightly better than the Agresti-Coull interval when the p isn't extreme.