---
title: "Chp1 Q20"
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
a).

* Sample for "intent to treat":

16402 healthy men and women between the ages of 18 and 30 years
in Rayong and Chon Buri provinces in Thailand.

* Sample for "per-protocol":

12542 healthy men and women (weren't HIV-positive on PCR before the trial started and received treatment according to the protocol) between the ages of 18 and 30 years in Rayong and Chon Buri provinces in Thailand.

* The population used in those studies:

community-based population with largely heterosexual risk.

* The population ultimately that the researchers would like to extend:

To use the results to advise the entire world.


b1). for intent-to-treat data
```{r}
#compute table value
c.table <- array(data = c(56, 76, 8146, 8124), dim = c(2,2), 
                 dimnames = list(Trt = c("vaccine", "placebo"), 
                                 Response = c("HIV", "No HIV")))

#We can use Odds Ratio to solve this problem
#Odds Ratio
OR.hat <- c.table[1,1]*c.table[2,2] / (c.table[2,1]*c.table[1,2])
round(OR.hat, 4) #OR.hat
round(1/OR.hat, 4) #inverse of OR.hat

alpha <- 0.05 #set 95% CI
var.log.or <- 1/c.table[1,1] + 1/c.table[1,2] + 
              1/c.table[2,2] + 1/c.table[2,1] #Variance of log(OR.hat)
OR.CI <- exp(log(OR.hat) + qnorm(p = c(alpha/2, 1-alpha/2)) *
               sqrt(var.log.or)) #Compute Wald CI for OR
round(OR.CI, 4) #95% CI for OR
rev(round(1/OR.CI, 4)) #inverse of 95% CI for OR
```

The estimated odd of contracting HIV is 73.49% as large as when the vaccine is given than when a placebo is given.

The 95% CI is (0.5196 < OR < 1.0392). Because 1 is within the interval, there is insufficient evidence to indicate the vaccine does decrease the true odds of contracting HIV

Alternatively, we could interpret the inverted odds ratio in terms of protection due to vaccination: The estimated odds of being HIV free are 1.3608 times as large as when the vaccine is given than when the placebo is given. The 95% confidence interval for the inverted odds ratio is (0.9623, 1.9244).


b2). for per-protocol data
```{r}
#compute table value
c.table <- array(data = c(36, 50, 6140, 6316), dim = c(2,2), 
                 dimnames = list(Trt = c("vaccine", "placebo"), 
                                 Response = c("HIV", "No HIV")))

#We can use Odds Ratio to solve this problem
#Odds Ratio
OR.hat <- c.table[1,1]*c.table[2,2] / (c.table[2,1]*c.table[1,2])
round(OR.hat, 4) #OR.hat
round(1/OR.hat, 4) #inverse of OR.hat

alpha <- 0.05 #set 95% CI
var.log.or <- 1/c.table[1,1] + 1/c.table[1,2] + 
              1/c.table[2,2] + 1/c.table[2,1] #Variance of log(OR.hat)
OR.CI <- exp(log(OR.hat) + qnorm(p = c(alpha/2, 1-alpha/2)) *
               sqrt(var.log.or)) #Compute Wald CI for OR
round(OR.CI, 4) #95% CI for OR
rev(round(1/OR.CI, 4)) #inverse of 95% CI for OR
```

The estimated odd of contracting HIV is 74.06% as large as when the vaccine is given than when a placebo is given.

The 95% CI is (0.4819 < OR < 1.1384). Because 1 is within the interval, there is insufficient evidence to indicate the vaccine does decrease the true odds of contracting HIV

Alternatively, we could interpret the inverted odds ratio in terms of protection due to vaccination: The estimated odds of being HIV free are 1.3502 times as large as when the vaccine is given than when the placebo is given. The 95% confidence interval for the inverted odds ratio is (0.8784, 2.0753).