---
title: "Chp5 Q17"
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

a).
```{r}
y <- c(0:10)
yhat <- 2
pear <- (y-yhat)/sqrt(yhat)
```

b).
```{r}
pp <- 1-ppois(y,yhat)
pn <- 1-pnorm(pear)
```

c). 
```{r}
yhat_2 <- format(cbind(y,pear,pp,pn),scientific=FALSE,digits = 1)
yhat_2
```
There is no Pearson residuals below 2 that have probability < 0.05
There is no Pearson residuals above 2 that have probability > 0.05

d). Standardized residuals can be interpreted approximately as observations from a standard normal distribution. When y_hat=2 and y<-c(0:10), the pearson residuals inputted do not contain extreme values.



e).
```{r}
y <- c(0:10)
yhat <- 1
pear <- (y-yhat)/sqrt(yhat)

pp <- 1-ppois(y,yhat)
pn <- 1-pnorm(pear)

yhat_1 <- format(cbind(y,pear,pp,pn),scientific=FALSE,digits = 1)
yhat_1


y <- c(0:10)
yhat <- 0.5
pear <- (y-yhat)/sqrt(yhat)

pp <- 1-ppois(y,yhat)
pn <- 1-pnorm(pear)

yhat_0.5 <- format(cbind(y,pear,pp,pn),scientific=FALSE,digits = 1)
yhat_0.5


y <- c(0:10)
yhat <- 0.25
pear <- (y-yhat)/sqrt(yhat)

pp <- 1-ppois(y,yhat)
pn <- 1-pnorm(pear)

yhat_0.25 <- format(cbind(y,pear,pp,pn),scientific=FALSE,digits = 1)
yhat_0.25


y <- c(0:10)
yhat <- 0.1
pear <- (y-yhat)/sqrt(yhat)

pp <- 1-ppois(y,yhat)
pn <- 1-pnorm(pear)

yhat_0.1 <- format(cbind(y,pear,pp,pn),scientific=FALSE,digits = 1)
yhat_0.1
```
Smaller y_hat leads to large pearson residuals. By repeating these steps, I don't feel comfortable using large pearson residuals. Because in those cases, Standardized residuals can't be interpreted approximately as observations from a standard normal distribution
