---
title: "Homework Assignment 4 part A"
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

```{r}
pol <- read.table(file = 
"C:\\Users\\Moon\\Desktop\\New folder\\pol_ideol_data.csv", 
                  header = TRUE, sep = ",")

pol$gender <- factor(x = pol$gender, levels = c("F", "M"))
pol$party <- factor(x = pol$party, levels = c("D", "R"))
pol$ideol <- factor(x = pol$ideol, levels = c("VL", "SL", "M", "SC", "VC"))
```

a). The estimated odd of being democratic is 38.18% as large as when the target is female than when the target is male.
```{r}
pol.table.a <- xtabs(formula = count ~ gender + party, data = pol)
Q1 <- pol.table.a[1,1]*pol.table.a[2,2] / (pol.table.a[2,1]*pol.table.a[1,2])
Q1
```

b).
```{r}
pol.table.b <- xtabs(formula = count ~ gender + party + ideol, data = pol)

Q2 <- pol.table.b[1,1,]*pol.table.b[2,2,]/ 
  (pol.table.b[2,1,]*pol.table.b[1,2,])
Q2
1/Q2
```
The estimated odd of being republican conditioning on very liberal is 22.72% as large as when the target is female than when the target is male.

The estimated odd of being republican conditioning on slightly liberal is 12.52% as large as when the target is female than when the target is male.

The estimated odd of being democratic conditioning on moderate is 60.5% as large as when the target is female than when the target is male.

The estimated odd of being democratic conditioning on slightly conservative is 47.43% as large as when the target is female than when the target is male.

The estimated odd of being democratic conditioning on very conservative is 47.82% as large as when the target is female than when the target is male.

c).
```{r}
mantelhaen.test(pol.table.b)
```
Give the p-value is a little larger than 0.05 and CI based on 95% is (0.98, 1.75). Strictly speaking, based on a 95% CI, we cannot conclude that the gender and party are not conditionally independent. However, based on 95% CI, we may say that there is a marginal evidence that gender and party are not conditionally independent.

d).
```{r}
#install.packages("DescTools")
library(DescTools)
BreslowDayTest(pol.table.b)
```
There is not strong evidence against Ho that all five ideologies have homogeneous conditional association. It is appropriate to pull data from all five ideologies together to increase study sample size to draw conclusion about gender and party.

